---
title:"Reproducible Pitch"
author: "Sai Gayathri J S"
date: '2022-03-19'
output: ioslides_presentation
---



```{r setup, include=FALSE, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coursera reproducible pitch

Your Shiny Application

Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

Deploy the application on Rstudio's shiny server

Share the application link by pasting it into the provided text box

Share your server.R and ui.R code on github

The application must include the following:

Some form of input (widget: textbox, radio button, checkbox, ...)

Some operation on the ui input in sever.R

Some reactive output displayed as a result of server calculations

You must also include enough documentation so that a novice user could use your application.

The documentation should be at the Shiny website itself. Do not post to an external link.

The Shiny application in question is entirely up to you. However, if you're having trouble coming up with ideas, you could start from the simple prediction algorithm done in class and build a new algorithm on one of the R datasets packages. Please make the package simple for the end user, so that they don't need a lot of your prerequisite knowledge to evaluate your application. You should emphasize a simple project given the short time frame.

## Regression models

URL: https://github.com/SaiGayathri0909/Developing-Data-Products/tree/main/WEEK%204%20Assignments

## Details
You can find all the details here
URL: https://github.com/SaiGayathri0909/Developing-Data-Products/tree/main/WEEK%204%20Assignments/Shiny%20App

## mtcars dataset

The data used was mtcars, which comes installed in R


## Source
Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

```{r}
library(datasets)
head(mtcars, 3)
```

---

## Analysis  - Main code
```r
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mpgData)  })
  ...
  output$fit <- renderPrint({
    summary(fit()) })
  
  output$mpgPlot <- renderPlot({
    with(mpgData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })  })
```

---

### Thank you